Clustering Analysis of Mobility Data

### 2018-07-09 dokumentation/submission.tex
kleine Fehler
Neural net Teil erweitert

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
%\usepackage{ngerman}
\usepackage[utf8x]{inputenc}
\usepackage{fancyvrb}
\usepackage{courier}
\usepackage{helvet}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{pdfpages}
\usetikzlibrary{calc}
\usepackage[strict]{changepage}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{cleveref}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta, automata, shapes, matrix,positioning}
\usepackage{amssymb}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{subcaption} 
\usepackage{float}
\usepackage{fixfoot}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{listings}

@@

	\subsection{Classification}
	\subsection{Neural Net}
	For all the neural net computations done we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\
	We do this, because results on the normal datasets had an unacceptable performance. An example is given in \Cref{fig: NN without vector}.	
	\begin{figure}
		\centering
		\includegraphics[scale = 0.4]{src/pic/NN_without_vector.png}
		\caption{An example of a neural net trained without person vector data.}
		\label{fig: NN without vector}
	\end{figure}

	In the following we consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	As an example of other strata aggregation we combine the stratas 1--2, 3--4 and 5--6 together and call them $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$. This builds a superset of the original stratas and since the stratas themselves are logically connected this task should be easier to fulfill.\\
	The sets are provided by the \texttt{testDataGenerator} from \Cref{sec: proprocessing}.
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		                         &   \#    &        & \multicolumn{3}{c|}{Set size} \\
		          Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
		    $\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
		 $\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
		   $\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
		%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
		   $\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
		$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
	\end{tabular}
	\caption{The accuracy values of the neural nets. (See excel-spreadsheet)}
	\label{tab: nn-accuracy}
	% mittels deep-learning-vector-average
	\end{figure}

	For each we performed 5 independent runs and take an average over those accuracy values in order to have a sophisticated statement.\\

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
%\usepackage{ngerman}
\usepackage[utf8x]{inputenc}
\usepackage{fancyvrb}
\usepackage{courier}
\usepackage{helvet}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{pdfpages}
\usetikzlibrary{calc}
\usepackage[strict]{changepage}
\usepackage{xspace}
\usepackage{hyperref}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta, automata, shapes, matrix,positioning}
\usepackage{amssymb}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{subcaption} 
\usepackage{float}
\usepackage{fixfoot}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{listings}

@@

	\subsection{Classification}
%	\input{MiriamClustering}
	\subsection{Neural Net}
	For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\

	We do this, because results on the normal datasets had an unacceptable performance, since only single movements and not complete paths of individuals are considered. An example training and performance measure is given in \Cref{fig: NN without vector} where unprocessed data is used. The performance is measured using 10-fold cross validation, i. e. the data is split into 10 subsets where in each iteration exactly one data set is used as test set and the other 9 as training set. The average value of the accuracy values lead
	 to the total accuracy value of the neural net.
	\begin{figure}[H]
		\centering
		\includegraphics[scale = 0.4]{src/pic/NN_without_vector.png}
		\caption{An example of a neural net trained without person vector data.}
		\label{fig: NN without vector}
	\end{figure}

	In the following we consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	As an example of other strata aggregation we combine the stratas 1--2, 3--4 and 5--6 together and call them $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$. This builds a superset of the original stratas and since the stratas themselves are logically connected this task should be easier to fulfill.\\

	For each neural net we are using equally distributed data sets with 100, 200 and the maximal amount of 595 individuals per strata which are provided by the \texttt{testDataGenerator} from \Cref{sec: proprocessing}. For every neural net and every set size we performed 5 independent runs and calculated the average over those accuracy values in order to have a sophisticated, comparable statements. 
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		                         &   \#    &        & \multicolumn{3}{c|}{Set size} \\
		          Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
		    $\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
		 $\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
		   $\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
		%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
		   $\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
		$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
	\end{tabular}
	\caption{The accuracy values of the neural nets. (See excel-spreadsheet)}
	\label{tab: nn-accuracy}
	% mittels deep-learning-vector-average
	\end{figure}
